Figures

### 2019-06-20 figures/07_model-selection.Rmd
hu4 lines

>>>>

dt        <- readRDS("../data/dt_scaled.rds") %>%
  mutate(signif_hu4 = hu4_zoneid %in% signif_hu4_ids) %>%
  tidyr::gather(key = "key", value = "value", 
                      -lagoslakeid, -hu4_zoneid, -hu12_zoneid, -signif_hu4, -tn) %>%
  dplyr::filter(key %in% c("maxdepth", "tn", "soil_org_carbon",
                                 "buffer_cultivated_crops", "corn",
                                 "nitrogen_fertilizer_use"))

ggplot(data = dt) + 
  geom_point(aes(x = tn, y = value, color = signif_hu4)) +
  geom_line(stat = "smooth", method = lm, se = FALSE, 
            aes(x = tn, y = value, color = signif_hu4)) +
  facet_wrap(~key)

dt        <- readRDS("../data/dt_scaled.rds") %>%
  mutate(signif_hu4 = hu4_zoneid %in% signif_hu4_ids) %>%
  tidyr::gather(key = "key", value = "value", 
                      -lagoslakeid, -hu4_zoneid, -hu12_zoneid, -signif_hu4, -tn) %>%
  dplyr::filter(key %in% c("wetland_potential", "tp",
                                   "nitrogen_atmospheric_deposition",
                                   "hu12_baseflow_mean", "clay_pct"))

ggplot(data = dt) + 
  geom_point(aes(x = tn, y = value, color = signif_hu4)) +
  geom_line(stat = "smooth", method = lm, se = FALSE, 
            aes(x = tn, y = value, color = signif_hu4)) +
  facet_wrap(~key)
